---
title: "Report on Gun Murders"
author: "Neel Mukhopadhyay"
date: "`r format(Sys.Date())`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is a report on 2010 gun murder rates obtained from FBI reports. The original data was obtained from [this Wikipedia page](https://en.wikipedia.org/wiki/Murder_in_the_United_States_by_state).

We are going to use the following library:

```{r loading-libs, message=FALSE}
library(tidyverse)
```
  
and load the data we already wrangled:

```{r}
load("rda/murders.rda")
```

## Murder rate by state

We note the large state to state variability by generating a barplot showing the murder rate by state:

```{r murder-rate-by-state, echo=FALSE}
murders %>% mutate(abb = reorder(abb, rate)) %>%
  ggplot(aes(abb, rate)) +
  geom_bar(width = 0.5, stat = "identity", color = "black") +
  coord_flip()
```

## A Very Important Note

Always save your R markdown files in the main project folder; do NOT create a separate sub-folder for your .Rmd files. This will cause errors in the relative directories you use to load data.